---
title: "Modified Milk Formula (f75) and outcomes for Children with Severe Acute Malnutrition"
output: html_document
author: "Daniel Trudell, Wendy Lee, and Natalie Block"
date: '`r format(Sys.time(), "%B %d, %Y")`'
params:
  print: FALSE
---

```{r, setup, include=FALSE} 
knitr::opts_chunk$set(echo = params$print, message=FALSE, warning=FALSE)

```

# Introduction
This data is from a randomized trial testing whether a modified milk formula (f75) improves outcomes for children with severe acute malnutrition. Our analyses includes a table with demographic information, a graph with weight at different stages of the study, and a graph with mid-upper arm circumference (MUAC) at different stages of the study. MUAC is used as a tool to diagnose malnutrition in infants.


# Table
## Summary of Demographic Information
```{r, table1}
#load dataset
here::i_am("report.rmd")
table1<-readRDS(here::here("output/table1.rds"))

table1
```

# Figures
## Boxplot of MUAC by Treatment Group
This box plot shows the average MUAC for each treatment group at three different time points in the study: MUAC is measured at baseline, MUAC1 is measured at stabilization, MUAC2 is measured at discharge/death/widthdraw.

```{r, graph1}
graph1<-readRDS(here::here("output/graph1.rds"))
print(graph1, height=7, width=10)
```

## Boxplot of Weight by Treatment Group
This box plot shows the average weight for each treatment group at three different time points in the study: weight is measured at baseline, weight1 is measured at stabilization, weight2 is measured at discharge/death/widthdraw.

```{r, graph2}
graph2<-readRDS(here::here("output/graph2.rds"))
print(graph2, height=7, width=10)
```
```